A new breeding crossover approach for evolutionary algorithms

### 2023-09-22 paper.tex
Late night update.

    We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10. In function F6, only for the 30-dimension difficulty, the canonical OPx alternative surpassed our proposal in the statistical test for the first occasion. On the following function, F7, only for the 10-dimension, our proposed CRx outperforms its alternative through the statistical test. Moreover, for functions F8 and F9 for both dimensions, the statistical test found better results for our proposed CRx strategy. For the function F10, the opposite of the previous function occurred, where for both dimensions, the classic OPx strategy obtained better results than our proposal. We describe the results in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15. At function F11, only for the 10-dimension, the original OPx passed the statistical test compared to our proposed strategy. For function F12, the CRx strategy found better results for both tested dimensions than the canonical alternative, passing the statistical test. Our proposed strategy proved a better alternative for the F13, F14, and F15 functions at the 30 dimensions test run. We continue describing the results shown in Figure~\ref{fig.experiment_F16-F20}, which includes functions F16 to F20. At function F16, both alternatives obtained similar results on both tested dimensions. While for function F17 only for the 10-dimension, our proposed strategy proved better. On the other hand, at functions F18 and F19, only at the 30-dimension test, our proposed CRx passed the statistical test. Finally, for function F20, both crossover alternatives tested equivalent results.

    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions f21 through F25.

>>>>

    We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10. In function F6, only for the 30-dimension difficulty, the canonical OPx alternative surpassed our proposal in the statistical test for the first occasion. On the following function, F7, only for the 10-dimension, our proposed CRx outperforms its alternative through the statistical test. Moreover, for functions F8 and F9 for both dimensions, the statistical test found better results for our proposed CRx strategy. For the function F10, the opposite of the previous function occurred, where for both dimensions, the classic OPx strategy obtained better results than our proposal. We describe the results in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15. At function F11, only for the 10-dimension, the original OPx passed the statistical test compared to our proposed strategy. For function F12, the CRx strategy found better results for both tested dimensions than the canonical alternative, passing the statistical test. Our proposed strategy proved a better alternative for the F13, F14, and F15 functions at the 30 dimensions test run. We continue describing the results shown in Figure~\ref{fig.experiment_F16-F20}, which includes functions F16 to F20. At function F16, both alternatives obtained similar results on tested dimensions. While for function F17 only for the 10-dimension, our proposed strategy proved better. On the other hand, at functions F18 and F19, only at the 30-dimension test, our proposed CRx passed the statistical test. Finally, for function F20, both crossover alternatives tested equivalent results.

    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions F21 through F25. Results obtained at F21 show that only at 30 dimensions did our proposed strategy prove statistically better. Where at F22 on the 10-dimension, the original OPx was the best, for the 30-dimension, our proposed CRx was declared the winner. On the next F23, the OPx proved better for both tested dimensions. At function F24, on the lower 10-dimension, the CRx was a clear victor, while at the 30-dimension, the original OPx was the most precise. The canonical strategy was the most suitable alternative for the last test operation, F25, only at the 30-dimension.
